Who will win the US 2024 election?!!

### 2024-03-14 paper/paper.qmd
added changes to abstract and intro

---
title: "Who will win the US 2024 election?!!"
author:
  - Monica Sainani
  - Kaavya Kalani
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "This study investigates the dynamics of voting behaviour during the US presidential election in 2022 using
 data from the American Community Survey(ACS) 2022 sample.

 We look at the correlation between voting preferences and demographic, socioeconomic, and geographic factors,
 such as age, income, education, state of residency, and gender.

@@

# Introduction
A key turning point in the political environment of the United States occurred with the 2022 presidential election,
which was marked by extreme conflict and serious economic and social challenges. We analyze data from the American
Community Survey (ACS) 2022 sample, which offers a thorough understanding of demographic, socioeconomic, and geographic
aspects across the nation, in order to comprehend the patterns underlying voting choices during this 2024 election
period.

@@

##Introduction to the Data:
With a focus on the American Community Survey (ACS) 2022 sample,
we present a summary of the dataset utilized in our statistical research study in this part.

@@

## Introduction to the Variables
These are he key variables utilized in our statistical analysis of voting behavior during the 2022 presidential
election. These variables are drawn from the American Community Survey (ACS) 2022 sample and encompass demographic,
socio-economic, and geographic characteristics that may influence individuals' voting preferences.

@@

>>>>

---
title: "Who will win the US 2024 election?!!"
author:
  - Monica Sainani
  - Kaavya Kalani
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "This study investigates the dynamics of voting behaviour using data from the American Community Survey(ACS)
2022 sample and predicting what the results would be for the 2024 Election.

 We look at the correlation between voting preferences and demographic, socioeconomic, and geographic factors,
 such as age, family income, education, state of residency, and sex.

@@

# Introduction
A key turning point in the political environment of the United States occurred with the 2020 presidential election,
which was marked by extreme conflict and serious economic and social challenges. We analyze data from the American
Community Survey (ACS) 2022 sample, which offers a thorough understanding of demographic, socioeconomic, and geographic
aspects across the nation, in order to comprehend the patterns underlying voting choices during this 2024 election
period.

@@

##Introduction to the Data:
We will use the most recent American Community Survey, the 2022 Sample, as the post-stratification dataset
to represent the voter population and adjust the weight of the survey data. The population for this sample was the
entire US population, categorized into households as subgroups, and the responses of the sampled subgroups were collected.
ACS 2022 dataset consists of 3,373,378 observations.

@@

## Introduction to the Variables
These are the key variables utilized in our statistical analysis of voting behavior during the 2022 survey.
These variables are drawn from the American Community Survey (ACS) 2022 sample and encompass demographic,
socio-economic, and geographic characteristics that may influence individuals' voting preferences.

@@

Cleaning process:
